\thetitle

### 2013-04-19 tfpie/tfpie.tex
abstract

\begin{abstract}
We propose a bridge between functional and object-oriented programming
in the first-year curriculum.
\end{abstract}

>>>>

\begin{abstract}
We propose a bridge between functional and object-oriented programming
in the first-year curriculum.  Traditionally, curricula that begin
with functional programming transition to a professional, usually
object-oriented, language in the second course.  This transition poses
numerous obstacles to students, and often results in confusing the
details of development environments, syntax, and libraries with the
fundamentals that the course focuses on.  Our proposal instead begins
the second course with a sequence of custom teaching languages which
minimize the transition from the first course, and allow students to
focus on the core ideas.  We then transition to Java half-way through
the course, at which point students have a strong command of the basic
ideas.  We have 3 years of experience with this course, and it has
produced notable success.
\end{abstract}
